decompr: GVC decomposition in R

### 2015-01-29 draft.Rnw
is it

\section{Introduction}
\epigraph{Hello....is is me you're looking for?}{Lionel Richie}
Global Value Chains (GVCs) have become a central topic in research on trade and development policy.
Both policy makers and academia increasingly value the growth opportunities GVCs offer to global trade and, especially, to developing countries.
However, analysing this phenomenon empirically requires complex matrix manipulations, since the relevant data is only available in the form of gross flows.
This package enables researchers with little background in matrix algebra and linear programming to easily derive standard GVC indicators for statistical analysis.

>>>>

\section{Introduction}
\epigraph{Hello?\\...\\ is it me you're looking for?}{Lionel Richie}
Global Value Chains (GVCs) have become a central topic in research on trade and development policy.
Both policy makers and academia increasingly value the growth opportunities GVCs offer to global trade and, especially, to developing countries.
However, analysing this phenomenon empirically requires complex matrix manipulations, since the relevant data is only available in the form of gross flows.
This package enables researchers with little background in matrix algebra and linear programming to easily derive standard GVC indicators for statistical analysis.
